Single \& double transits discovered in the \kepler\ archive: \\ the frequency of long-period exoplanets

### 2016-02-18 document/ms.tex
section headings

\title{%
The occurrence rate of long-period exoplanets
}

@@

\section{The fully-automated search for long-period exoplanets}

@@

\paragraph{Pixel-level}

Blah.

\paragraph{Auxiliary data}

Blah.

\section{Data selection \& preparation}\sectlabel{data}

@@

\section{Results}

@@

\section{Completeness \& reliability}

@@

>>>>

\title{%
Single \& double transits discovered in the \kepler\ archive: \\
the frequency of long-period exoplanets
}

@@

\section{The fully-automated search for long-period transiting exoplanets}

@@

\section{A catalog of exoplanet \& binary candidates}

\subsection{Target selection}\sectlabel{data}

@@

\subsection{Parameter estimation}

@@

\subsection{Discussion of some interesting systems}

\section{Empirical search completeness}

@@

\section{Astrophysical false positives}

Tim to write some words here.
